---
title: |  
      | Introduction to Statistical Analysis
      | MSSA 70200
format:
  pdf:
    colorlinks: true  
    fontfamily: libertinus
pdf-engine: pdflatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval = TRUE, message = FALSE, warning = FALSE, comment = "")
```


# Email: seth.berry@nd.edu

# Office: 337 Mendoza

# Course Objectives

By the end of the course, you will be able to:

-   Be a fearless R user

-   Create and test hypotheses

-   Apply regression models to answer questions

# Course Activities

## Readings

There is no *official* textbook for this course. There will, however, be readings from a few different texts posted for each topic. 

## Class Flow

We will use our class time to *extend, discuss, and practice*. We will use a variety of different techniques to share our ideas with each other and the class as a whole.

## Class Exercises

You don't learn how to model by reading about it (but references help), watching other people do it, or watching YouTube videos. The only way to learn how to analyze data is by doing it; as such, the majority of our class time will be spent working together on modeling techniques.

## Homework

There will be three assignments which will be graded; these assignments will come from the major topics within our class. Homework will be assigned on Thursdays and due the Monday before class. Each person should turn in their own assignment, but you are absolutely free to collaborate with people in class. Collaboration does not mean copying -- it means that you have worked together to solve the problem and both people have their own unique answers to the problem. If work looks like it has been copied from another student or online source, it will be given a 0. It is advised to start the assignments early and bring questions to office hours.

### Code Assistance

You cannot use code produced by any Large Language Model (LLM). Code that looks like it has been generated by ChatGPT, Copilot, or any other model will be subjected to intense scrutiny and the probability of getting a 0 for that work is very high. 

## Final Presentation

As individuals, you will find data, generate questions, and give a presentation over your findings. Each person will be given 3 minutes to present. 

# Grading

Daily work -- 100 points

Homework -- 100 points

Final presentation -- 100 points

Total -- 300 points

# Schedule

```{r, results='asis'}
library(dplyr)
data.frame(
  Date = c("06/18 (T)", 
           "06/19 (W)", 
           "06/20 (R)*", 
           "06/25 (T)", 
           "06/26 (W)", 
           "06/27 (R)*", 
           "07/09 (T)", 
           "07/10 (W)", 
           "07/11 (R)*",
           "07/23 (T)",
           "07/24 (W)",
           "07/25 (R)", 
           "07/30 (T)",
           "07/31 (W)"), 
  Topic = c("Introduction to R", 
            "R Basics",
            "Probability and Distributions*",
            "Visualizations",
            "Hypothesis Testing",
            "Linear Regression*",
            "Multiple Regression",
            "Statistical Interactions", 
            "Model Diagnostics*",
            "Logistic Regression", 
            "Mixed Effects", 
            "Final Project Work Day", 
            "Final Project Work Day",
            "Final Project Presentations")
) %>% 
  stargazer::stargazer(., summary = FALSE, header = FALSE, title = "Tentative Schedule", 
                       rownames = FALSE, notes = "* denotes homework is assigned.")
```